---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## mypackage
<!-- badges: start -->
[![R-CMD-check](https://github.com/Gyijun/mypackage/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Gyijun/mypackage/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/Gyijun/mypackage/branch/master/graph/badge.svg)](https://app.codecov.io/gh/Gyijun/mypackage?branch=master)
<!-- badges: end -->

## Overview

The goal of mypackage is to calculate covariances and pearson correlation between two vectors or columns of matrices. 

-   `modified_cov()` conducts covariances computing between vectors and columns of matrices with complete cases

-   `modified_cor()` conducts pearson correlation computing between vectors and columns of matrices with complete cases

The calculation is conducted based on the following fomulas:

$$
\begin{aligned}
&cov(X,Y)=E[(X- μ_{x})(Y-μ_{y})]\\
&r_{xy}=\frac{\sum\limits_{i=1}^n(x_{i}-\bar{x})(y_{i}-\bar{y})}{(n-1)s_{x}s_{y}}\\
\end{aligned}
$$

## Installation

You can install the development version of `mypackage` from [GitHub](https://github.com/) with:

``` {r}
#install.packages("devtools")
#library(devtools)
devtools::install_github("Gyijun/mypackage", build_vignettes = T)
```
To install `mypackage`, you might also need to install `devtools` package. See detailed instruction in the [tutorial](https://github.com/Gyijun/mypackage/blob/master/vignettes/mypackage.Rmd) .


## Usage

You can load `mypackage` by the following codes:

```{r }
library(mypackage)
```

## Basic examples

Here are some basic examples to apply `modified_cov()` and `modified_cor()`:

```{r }
# covariance computing
(cov<-modified_cov(matrix(c(rnorm(100,0,1),c(rnorm(100,0,1)),2,100))))

#pearson correlation computing
(cor<-modified_cor(c(rnorm(100,0,1)),c(rnorm(100,0,1))))

```
