---
title: "Introduction to mypackage"
output: rmarkdown::html_vignette
author: 
   -Yijun Guo
   
description: >
  Start here if this is your first time using mypackage. You'll learn how the functions can be
  applied to calculate covariances and pearson correlations for complete matrix,data frame and
  vectors. This vignette will also show how the functions in mypackage compare to base R
  functions with complete cases and method option "pearson".
  
vignette: >
  %\VignetteIndexEntry{mypackage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup,include=FALSE}
library(mypackage)
library(devtools)
library(bench)
```


## Quick Start:

This part will briefly go over the main functions and introduce the basic operations and outputs.

## Installation:

*  `mypackage` is based on [R] (>= 3.5.0), and can be downloaded from github.

*  To install `mypackage`, you might need to install `devtools` package first.Following steps can be taken:

   (1) Set up the working development environment as follows and install release version of devtools from CRAN:

     *- Windows*: Install [Rtools](https://cran.r-project.org/bin/windows/Rtools/).

     *- Mac*: Install [Xcode](https://developer.apple.com/xcode/) from the Mac App Store.

     *- Linux*: Install a compiler and various development libraries (details vary across differnet flavors of Linux).

   (2)  Here are example codes for installation on Windows system:
   
   - Installation of devtools
   
```{r}
#install.packages("devtools",repos = "http://cran.us.r-project.org")
#library(devtools)
#library(usethis)
#devtools::install_github("Gyijun/mypackage", build_vignettes = T)
```
   
   - Installation of mypackage
   
```{r}
#devtools::install_github("Gyijun/mypackage", build_vignettes = T)
```
   

## Loading the package:

```{r}
#library(mypackage)
```

* The function `modified_cov` returns covariances of two vectors or columns of matrices/data frames.

* The function `modified_cor` returns pearson correlations of two vectors or columns of matrices/data frames.

## Arguments

As for argument, x must be provided in numeric vector/matrix/data frame form, y is defaulted to be NULL and can be vector/matrix/data frame. However, y must be provided when x is in vector form. y and x should have compatible dimensions and complete cases.

## Usage

If matrices are provided in inputs:
```{r}

```

When data frames are provided:
```{r}

```

When x,y are both vectors:
```{r}

```

It should be noticed that when both x,y only contain 1 element,the output will be NaN.
```{r}

```

When y is NULL(defult), calculation can be conducted between columns of x.
```{r}

```



If matrices/dataframes/vectors are provided in inputs:
```{r}

```

Like modified_cov, if both x,y only contain 1 element,the output will be NaN.
```{r}

```


## Error interpretation:

There are a few error conditions for modified_cov and modified_cor functions.

When only one item is provided in vector form, the calculation can not be conducted:
```{r}

```

Since the functions are designed for complete cases, there couldn't be missing value in the given vector and matrices,eg:

```{r}
#x3<-matrix(runif(5000,min=0,max=100),20,50)
#x3[10,6]=NA
#modified_cov(x3) # Error: missing observations in cov/cor
```


If both x,y are provided, then they should have compatible dimensions for matrix production operations.Incompatible dimensions will lead to error:
```{r}

```

Numeric arguments(or logical) are expected as inputs. Inputs with character elements or are not atomic vectors can not be calculated.
```{r}
#modified_cov(c(1,"def",TRUE,"abc"),c(1,2,3,4)) # Error: ((is.numeric(x) || is.logical(x)) & is.atomic(x)) is not TRUE
```


## Comparation with base R codes:

This part compares mypackage functions to their base R equivalents. This shows users the difference and restrictions on using mypackage function comparing to base R functions. It also helps users to know how the functions perform on accuracy and effectiveness compared to original functions.
```{r}

```

   


